\documentclass{mycv}

\name{Asher Mancinelli}
% \address{DLB 625, Department of Computer Science \\ Hong Kong Baptist University, Hong Kong}
\address{Pacific Northwest National Laboratory \\ 902 Battelle Boulevard \\ Richland, WA  99352  USA}
\email{asher.mancinelli@pnnl.gov}
\github{ashermancinelli}
\linkedin{asher-mancinelli-bb4a56144}

\begin{document}

\maketitle

\section{Research \\ Interests}

I am interested in low-level code optimization, concurrency, distributed systems, and systems programming.
My current focuses include:

\begin{itemize}
  \item Smooth and sustainable ports of CPU-bound HPC codes to GPUs.
  \item Memory safety in distributed systems.
  \item Concurrent design patterns.
  \item Performance tuning.
\end{itemize}

\section{Professional \\ Experience}

\subsection{Pacific Northwest National Laboratory}[Richland, WA USA]
\begin{positions}
  \entry{Software Development Lead}{April 2020~--~Present}
  \entry{HPC Software Developer}{June 2019~--~March 2020}
  \entry{Machine Learning/HPC Software Developer}{June 2018~--~June 2019}
\end{positions}

\begin{itemize}
  \item Led development team to port high-performance linear solver to run on GPUs.
  \item Led hackathons of 40+ members of 5+ national laboratories to port power-grid simulations to GPU.
  \item Increased performance of a biological simulation by ~$2,500\%$ (from 2 weeks to 8 minutes).
  \item Increased performance of an LED simulation by ~$15,000\%$ (from 6 weeks to 4 minutes).
  \item Optimization work described as \textit{the posterchild for how PNNL should operate} by a panel of external collaborators.
  \item Reproduced closed-source research with a seq-2-seq neural network for OCR (\textit{Rosetta} network).
  \item Invented new algorithm for an \verb!MPI_Gatherv! call (tree-based reduction algorithm).
  \item Led many training sessions on code optimization and HPC techniques at PNNL.
  \item Gave several talks about optimizing research code and making inter-language interfaces perform well.
\end{itemize}

\subsection{Micron Technologies}[Washington D.C. Metro Area]
\begin{positions}
  \entry{Data Science \& Analytics Intern}{June 2017~--~August 2017}
\end{positions}

\begin{itemize}
  \item Invented algorithm to cluster wafer defects increasing company profit by significant margin.
  \item Wrote random-forest model to filter large amounts of financial data to increase bargaining power of procurement department.
  \item Trained time-series ML model to predict server failure decrease server downtime.
\end{itemize}

\section{Education}

\subsection{Eastern Washington University}[Cheney, WA]
\vspace{-\parskip}%
\begin{itemize}[label={}]
  \item Bachelors of Science in Computer Science, minor in Mathematics \printdate{September 2016~--~March 2020}
  \item Graduated with \textit{magna cum laude}
  \item Member of Dean's List
  \item Received three scholarships for exceptional performance in the Math dept.
  \item Placed $1^{st}$ in Whitworth University's programming competition \textit{PineCodes}. \printdate{2019}
\end{itemize}

\section{Skills}

\begin{description}
  \item[Programming] C/C++, CUDA, MPI, Rust, Python, \LaTeX, Bash
  \item[Tools] Vim, Tmux, Git, macOS, Linux
  \item[Soft Skills] Public speaking, technical writing, editorial review
\end{description}

\section{Misc}

\begin{itemize}
  \item Gave talk at \href{https://fullstacktc.org/user/ashermancinelli}{ \underline{ local developer meetup } }. \printdate{2017}
  \item Member of technical editorial review board for Brett Slatkin's \textit{Effective Python}. \printdate{2019}
  \item Contributor to various open-source projects, such as \textit{PyTorch}, \textit{ElasticSearch}, and \textit{Hiop} (see GitHub profile).
\end{itemize}
% \section{Talks}
% 
% \begin{enumerate}
%   \item Blockchain Privacy Preserving Techniques, \emph{The 36th CCF National Database Conference}, Jinan, China, Oct.~2019.
%   \item Towards Searchable and Verifiable Blockchain, \emph{1st Workshop on Blockchain and Data Management at 35th IEEE International Conference on Data Engineering}, Macau, Apr.~2019.
%   \item When Query Authentication Meets Fine-Grained Access Control: A Zero-Knowledge Approach, \emph{2018 ACM SIGMOD International Conference on Management of Data}, Houston, USA, Jun.~2018.
% \end{enumerate}

%\section{Awards}
%
%\begin{itemize}
%  \item SIGMOD Travel Award, ACM \printdate{2018}
%  \item Department RPg Performance Award, Hong Kong Baptist University \printdate{2018,~2019}
%  \item Postgraduate Research Symposium Best Research Performance Award \& Best Poster Award, Hong Kong Baptist University \printdate{2018}
%  \item Yakun Scholarship Scheme for Mainland Postgraduate Students, Hong Kong Baptist University \printdate{2018}
%  \item Excellent Teaching Assistant Performance Award, Hong Kong Baptist University \printdate{2017}
%  \item Teaching Assistant Performance Award, Hong Kong Baptist University \printdate{2015,~2016}
%\end{itemize}

\end{document}
